Draft_markdown_v1

### 2024-04-08 Draft_V1.Rmd
Update Draft_V1.Rmd

```{r}
filtered_samp_nrc_party %>%
  ggplot(aes(date, ratio, color = party)) +
  geom_point(alpha=0.25) +
  geom_smooth(method="loess", se = F, alpha=0.25, size = 1.5) +
  labs(y = "Sample NRC sentiment negative ratio by party", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red", size = 1) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

>>>>

```{r}
filtered_samp_nrc_party %>%
  ggplot(aes(date, ratio, color = party)) +
  geom_point(alpha=0.25) +
  geom_smooth(method="loess", se = F, alpha=0.25, size = 1.5) +
  labs(y = "Sample NRC sentiment negative ratio by party", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red", size = 1) + 
  annotate("text", x = as.Date("2007-09-24"), y = 5, label="Northern Rock\nLiquidity Support", angle=90, color = "black", size = 4)
  theme_minimal() +
  theme(legend.position = "bottom")
```
